---
title: "InClass05_data_cleaning_ptt_lubridate"
author: "Jilung Hsieh"
date: "9/22/2019"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Practice Notes
- Goals: lubridate, stringr, ggplot2, plotting timeline
- Related: 
- Unknown: Crawler designs


# Questions
- How do you clean the raw data of Hang's related posts?
- How to 

# Loading packages
```{r}
library(lubridate)  # for processing time
library(tidyverse)
options(stringsAsFactors = F)
```

# Loading data
```{r}
load("data/HatePolitics_韓_201906010320_raw.rda")
```


# Related sources
- [The lubridate packages document](https://rdrr.io/cran/lubridate/man/lubridate-package.html)
- [Usage: [Stackoverflow] dplyr, lubridate : how to aggregate a dataframe by week?](https://stackoverflow.com/questions/40554231/dplyr-lubridate-how-to-aggregate-a-dataframe-by-week)
- [lubridate cheatsheets](https://evoldyn.gitlab.io/evomics-2018/ref-sheets/R_lubridate.pdf)


# Parsing character to POSIXct R data time object

## By base packages
- Using `?strptime` to find formatter
- %a: bbreviated weekday name
- %b: Abbreviated month nam
- %e: Day of the month as decimal number (1–31)
- %X: Time. Locale-specific on output, "%H:%M:%S" on input.
- %Y: Year with century

```{r}
# Given a character timestamp
t <- "Fri Apr 12 09:12:40 2019"

# Converting t to POSIXlt by strptime()



# Converting t to POSIXlt to POSIXct by strptime() and as.POSIXct()



```

## By lubridate packages
- a: Abbreviated weekday name in the current locale
- b!: Abbreviated or full month name in the current locale.
- d!: Day of the month as decimal number (01–31 or 0–31)
- H: HOUR
- M: MINUTE
- S: SECOND
- Y!: Year with century

```{r}
# Converting the character time to datetime by lubridate::parse_date_time()



```

## Time zone
- CST - Central Standard Time (UTC+8)
- UTC - Coordinated Universal Time
- GMT


```{r}
# Parsing datetime with time zone
parse_date_time("Fri Apr 12 09:12:40 2019", "ab!d!HMSY!", tz = "Asia/Taipei")
parse_date_time("Fri Apr 12 09:12:40 2019", "ab!d!HMSY!", tz = "America/New_York")

```



# Cleaning posts
- Using `parse_date_time()` to convert time character to POSIXct
- Using `drop_na()` to drop rows having NA in specific columns
- Using `filter()` to filter posts between 2019-01-001 and 2019-06-01
- Using `str_extract()` to extract poster id, or using `str_replace()`


```{r}








```

## Testing
```{r}
str_extract("sunyeah ( 湯元嗎)", "\\(.+\\)")
str_extract
```


# Plotting

## (Deprecated-old-style) by cut()
- `cut()` will turn datetime to factor for the new variable week

```
posts %>%
    mutate(week = cut(ptime, breaks = "week")) %>% glimpse()
    count(week) %>% 
    ggplot() + aes(week, n) +
    geom_col() +
    geom_vline(aes(xintercept = as_datetime("2019-02-02")), color="red", alpha=0.5)  
```


## as_datetime() level
- `geom_vline()` axis must be equivalent with x-axis

```{r}








```

## as_date() level
```{r}







```

## Color specific weeks
- `mutate()` one variable group as bar chart filling group
- Using `if_else()` to create binary choice of colors
- 
```{r}









```


# Cleaning comments and joining with filtered posts
```{r}




```


# Saving posts and comments to an rda with date time
```{r}
format(now(), "%Y%m%d_%H%M")

```




