---
title: "InClass04_join_ptt"
author: "Jilung Hsieh"
date: "9/22/2019"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading libraries
```{r}
library(tidyverse)
options(stringsAsFactors = F)
```

# Loading data
```{r}
load("data/HatePolitics_Hang_20190101_2019_06_01.rda")
```

# Filtering posts by year >= 2019
```{r}
library(lubridate)
posts2019 <- posts %>% filter(year(ptime) >= 2019)
```


# Filter comments by selected posts (year >= 2019)
```{r}
comments2019 <- comments %>% right_join(posts2019, by = "plink")
```

# Filter posts with title category [新聞]
```{r}
posts %>% filter(str_detect(ptitle, "^\\[新聞\\]")) %>% head %>% knitr::kable()
```

# Computing number of comments of selected posts
- computing number of comments of posts with tilte starting with [新聞]
```{r}
comments %>%
    count(plink) %>%
    right_join(posts, by = "plink") %>%
    filter(str_detect(ptitle, "^\\[新聞\\]")) %>% head %>% knitr::kable()
```

# Computing number of comments for each post
```{r}
comments %>%
    count(plink) %>%
    right_join(posts, by = "plink") %>%
    filter(str_detect(ptitle, "^Re"))  %>% head %>% knitr::kable()
```

# Computing comment to poster relationship
```{r}
posts %>% select(plink, poster) %>%
    left_join(comments, by = "plink") %>%
    count(commentor, poster, sort = T) %>%  head %>% knitr::kable()
```


# Computer comment times to poster, each post counts one time.
```{r}
posts %>% select(plink, poster) %>%
    left_join(comments, by = "plink") %>%
    group_by(plink) %>%
    filter(!duplicated(commentor)) %>%
    ungroup() %>%
    count(commentor, poster, sort = T) %>%
    filter(!poster == "mark2165")  %>% head %>% knitr::kable()

```


```{r}
library(igraph)
library(ggraph)
posts %>% select(plink, poster) %>%
    left_join(comments, by = "plink") %>%
    group_by(plink) %>%
    filter(!duplicated(commentor)) %>%
    ungroup() %>%
    filter(!poster == "mark2165") %>%
    count(commentor, poster, sort = T) %>%
    slice(1:3000) %>%
    group_by(commentor) %>%
    filter(n() >= 20) %>%
    ungroup() %>%
    group_by(poster) %>%
    filter(n() >= 20) %>%
    ungroup() %>%
    graph_from_data_frame(directed = T) %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), color="dimgray") +
    geom_node_point(color = "gold", size = 2, alpha=0.5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1, color = "royalblue", alpha = 0.8) + 
    theme_void()

```







