---
title: "InClass04_join_ptt"
author: "Jilung Hsieh"
date: "9/22/2019"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Practice Notes
- Practice goals: Joining data
- Related: ggplot2, stirngr
- Unknown: lubridate, crawler


# Loading packages
```{r}
library(tidyverse)
options(stringsAsFactors = F)
```

# Loading data
```{r}
load("data/HatePolitics_Hang_20190101_2019_06_01.rda")
```

# Filtering posts by year >= 2019
```{r}
library(lubridate)
posts2019 <- posts %>% filter(year(ptime) >= 2019)
```


# Filter comments by selected posts (year >= 2019)
```{r}

```

# Filter posts with title category [新聞]
```{r}

```

# Computing number of comments of selected posts
- computing number of comments of posts with tilte starting with [新聞]
```{r}

```

# Computing number of comments for each post
```{r}

```

# Computing comment to poster relationship
```{r}

```


# Computer comment times to poster, each post counts one time.
```{r}

```


```{r}

```







