---
title: "R02_2 Pivot on tp theft"
author: "Jilung Hsieh"
date: "2019/9/2"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading CSV
## From the web
* 直接從網路上載入台北市竊盜案資料
* `df <- read.csv(url, fileEncoding = "big5")`這行的意思是把上面那個`url`用`read.csv()`這個函式讀取。讀取的同時，由於一般EXCEL為中文編碼`BIG5`，所以該文件八成是該台北市政單位還用EXCEL在編資料，所以要跟程式碼講說，這個網址所指到的檔案編碼為`BIG5`。
    * `fileEncoding = "big5"`稱為`read.csv()`這個函式的**參數(parameter)。

```{r}
library(httr)
url <- "http://data.taipei/opendata/datalist/datasetMeta/download?id=68785231-d6c5-47a1-b001-77eec70bec02&rid=34a4a431-f04d-474a-8e72-8d3f586db3df"
df <- read.csv(url, fileEncoding = "big5")
```

## Read CSV by read.csv() from local directory
- reading `tp_theft_.csv` in the subfolder `data`
- Remember to use the `fileEncoding` argument to `big5`
```{r}
# read.csv() to read csv and convert it to a data.frame
df <- read.csv("data/tp_theft.csv", fileEncoding = "big5")

# Checking the strcutrue of it
str(df)

```

## Setting `stringAsFactors`
```{r}
# Add stringsAsFactors argument  to avoid converting string to factor
df <- read.csv("data/tptheft.csv", fileEncoding = "big5", stringsAsFactors = FALSE)
# double-check the structure of it
str(df)
```

## Using `read_csv()` to read the csv
- remember to specify the `locale` argument to `big5`. `locale = locale(encoding = "Big5")`
```{r}


```




## (Option) Geting a file back to local directory
- 部分Mac電腦無法使用`read.csv()`從網路上取得資料又轉為`data.frame`，一個可行的辦法是先用`GET(url, write_disk("data/tptheft.csv"))`將其取回並命名為`data/tptheft.csv`，之後再用`df <- read.csv("data/tptheft.csv", fileEncoding = "big5", stringsAsFactors = FALSE)`直接讀取該檔案。

```{r}
library(httr)
GET(url, write_disk("data/tptheft.csv", overwrite = TRUE))
df <- read.csv("data/tptheft.csv", fileEncoding = "big5", stringsAsFactors = FALSE)
```


# Inspecting data
* `View(df)` 用RStudio所提供的GUI直接觀看變數
* `head(df)` 取前面六筆資料（也就是六列的資料來概觀該資料）
* `class(df)` 印出該
* `str(df)`

```{r}
# View(df)
head(df)	# get first part of the data.frame
class(df)
str(df)
summary(df)
# look up help
help(summary)
?summary

```



## Dimension
e.g., dim(), ncol(), nrow(),length()
```{r}
dim(df)
ncol(df)
nrow(df)
length(df)
```


## Variable names
* `names(df)`  列出變數名稱
* `df$發生.現.地點` 顯示該變數內容
* `df$發生時段` 顯示該變數內容
* `length(df$發生時段)` 顯示該變數的長度（相當於有幾個）

```{r}
names(df)
head(df$發生.現.地點)
head(df$發生時段)
length(df$發生時段)
```



# Cleaning data
* 目標：「發生時段」我打算取出前面的數字來代表時間就好，「發生地點」我打算只取出行政區名，其他地址不要。邏輯上，我要把那串字取出第x個字到第y個字，所以要用`substr()`這個函式，或者未來會教到的`stringr::str_sub()`函式。
* 用`?substr`查詢其用法和意義。相當於`getting sub string since x to y`。

```{r}
# Get substring of var "發生時段" and assign to a new time var
df$time <- substr(df$發生時段, 1, 2)


# Get substring of var "發生.現.地點" and assign to a new region var
df$region <- substr(df$發生.現.地點, 4, 5)
```



# Pivot analysis: Counting and Summarizing

* 我們要回答的第一個數據問題通常是，那XXX的案例有幾個？例如大安區有多少竊盜案？買超過10000元訂單的客戶有多少人？男生和女生會修程式課的個別有多少人？這稱為計數。

## Counting single variable by table()
```{r}
# counting the frequency of time variable
table(df$time)

# counting the frequency of region variable
table(df$region)
```



## Counting by tapply()
* Using `length()` as counting method
```{r}
# tapply() one arbitrary var by var time with length() function
tapply(df$編號, df$time, length)

# tapply() one arbitrary var by var region with length() function
tapply(df$編號, df$region, length)
```


# Filtering data
```{r}
# filter out irrelevant timestamp
df <- df[!df$time %in% c("00", "02", "06", "08", "12", "14" ,"18", "20"), ]

# filter out irrelevant region(area)
df <- df[!df$region %in% c("三重", "中和", "淡水", "板橋"), ]
```



# Pivot analysis on 2 vars

## by `table()` with 2 independent vars
```{r}

# Tabulating time and region variables
res_table <- table(df$time, df$region)

# Checking it class and its content
class(res_table)
res_table
```

## by `tapply()` with 2 independent vars
```{r}
res_tapply <- tapply(df$編號, list(df$time, df$region), length)
class(res_tapply)
res_tapply
# View(res)
```

# Pivot by dplyr::count()

```{r}
# counting by dplyr::count()
res_count <- dplyr::count(df, time, region)
class(res_count)
res_count

# spreading the region into columns
res_count_spread <- tidyr::spread(res_count, region, n, fill = 0)
res_count_spread
# ??dplyr::count
```


# Plotting

```{r}
# mosaicplot() to plot 2-dim categorical vars.
mosaicplot(res_table)

# Add argument main (figure title)
mosaicplot(res_table, main="mosaic plot")
```

## (Option) Cannot show Chinese?
```{r}
par(family=('Heiti TC Light'))
par(family=('STKaiti'))
mosaicplot(res_table, main="mosaic plot")
```

## (Option) Self-defined color?

```{r}
# Set up color by yourself.
colors <- c('#D0104C', '#DB4D6D', '#E83015',  '#F75C2F',
            '#E79460', '#E98B2A', '#9B6E23', '#F7C242',
            '#BEC23F', '#90B44B', '#66BAB7', '#1E88A8')
par(family=('STKaiti'))
mosaicplot(res_table, color=colors, border=0, off = 3,
		   main="Theft rate of Taipei city (region by hour)")
```

# Practices

## Practice02_2_1

* Check what happens if you swap the time and region in tapply()
* does it possible to extract month  by substr()?
* (you may need to search how to extract the last n characters in R)

```{r}
x <- df$發生.現.日期
df$month <- substr(x, 3, 4) # is this correct? Try to modify it!
# res2 <- tapply(df$編號, list(df$month, df$region), length)
# res2 <- tapply(df$編號, list(df$region, df$month), length)
# mosaicplot(res2, color=colors, border=0, off = 3, main="Theft rate of Taipei city (region by hour)")
```

## Practice02_2_2
* Reading maternal leave data
* Summarize the last year data by world region
```{r}

```


# (dplyr) on tp theft
```{r}
# readr::guess_encoding("data/tp_theft.csv")
library(readr)
library(tidyverse)
df <- read_csv("data/tp_theft.csv", locale = locale(encoding = "Big5")) %>% 
    select(id = 編號, 
           cat = 案類, 
           date = `發生(現)日期`, 
           time = `發生時段`, 
           location = `發生(現)地點`) %>% # glimpse()
    mutate(year = date %/% 10000) %>%
    mutate(month = date %/% 100 %% 100) %>%
    mutate(location = stringr::str_sub(location, 4, 6)) %>%
    # count(year) %>% View
    filter(year >= 104) %>%
    # count(time) %>% View
    filter(!time %in% c("00~02", "02~04", "06~08", "08~10", "12~14")) %>%
    # count(location) %>%
    filter(!location %in% c("中和市", "板橋市")) %>%
    count(time, location) %>%
    spread(location, n, fill=0) 
```


```{r warning=FALSE}
par(family=('STKaiti'))
row.names(df) <- df$time
df$time <- NULL
colors <- c('#D0104C', '#DB4D6D', '#E83015',  '#F75C2F',
            '#E79460', '#E98B2A', '#9B6E23', '#F7C242',
            '#BEC23F', '#90B44B', '#66BAB7', '#1E88A8')
mosaicplot(df, color=colors, border=0, off = 3, main="Theft rate of Taipei city (region by hour)")

```


