---
title: "R02_1 Paid Maternity Leave"
author: "Jilung Hsieh"
date: "2019/9/2"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Case: Paid Maternal Leave

* 本案例將利用R來重製華盛頓郵報在2016/08/13的一篇談論美國婦女產假支薪情形的報導。這個案例中將會應用到data.frame和基本的繪圖與資料摘要方法。The case adaped Washington Post's paid maternity leave as an exmaple to introduce basic skill of data.frame, plotting, and data mamipulation.

* 原始新聞來源：https://www.washingtonpost.com/news/worldviews/wp/2016/08/13/the-world-is-getting-better-at-paid-maternity-leave-the-u-s-is-not/?tid=sm_tw&utm_term=.f8cd50280326#comments


# Read .xlsx by readxl package

* readxl也包含在tidyverse的套件集中，所以應該已經在前次安裝過，不用特別安裝。
 
```{r}
# Loading the pkg to read excel

# Loading global option to avoid converting character vector to factor

```




# 0. Learner ver.

* Use `?read_excel` to see function, inputs and ouput of `readxl::read_excel()` 
* `read_excel()` can convert a sheet to a data.frame

```{r}
# use ?read_excel or help(read_exel) to check out the function

# read_excel(path, sheet = NULL, range = NULL, col_names = TRUE, col_types = NULL, na = "", trim_ws = TRUE, skip = 0, n_max = Inf, guess_max = min(1000, n_max))
```




# 1. Read and inspect data

```{r read excel}
# Import readxl package

# Use read_excel() to convert excel sheet to data.frame

```

# 2. Preview data by `View()`, `class()`, `dim()`, `str()`, `summary()` and `names()`

```{r preview data}
# View(df)



# Show names of variables (vectors, columns) by names()

```



# 3. Select essential variables

```{r}
# Select the 3rd and 6th to 24th columns


# Use class(), dim(), and str() to inspect the data



```



# 3. Replace NAs

* `NA: Not Available`
* `v[is.na(v)]` will select all NA cells
* 以0取代NA的資料格。避免繪圖產生錯誤
* `sum(is.na(matleave))`的目的是檢測還有沒有NA值。如果有的話`is.na()`就會是`TRUE`，那麼加總後，如果不是0，那就代表還有NA。

```{r}
# Use is.na() to detect NA element (TRUE/FALSE)


# Assign 0 to those NA data


# anyNA() to check if there are still NA cells.


# sum(is.na()) to count the number of NA



```



# 4.1 Filter data by the last year value

```{r}
# Use logical comparison to see if the last year equals to 5
# Assign matching row to var m5 when 2013 data(matleave_13 equals to 5


# nrow() to count matching data


# Is it possible to use length() to check the data length? If not, how to do it?
# matleave$'matleave_13'
# matleave$'matleave_13'==5
# length(matleave$'matleave_13'==5)
```




# 4.2 Filter data by the first year value

```{r}
# filter rows whose 'matleave_95' is 5, and assign to var m55


# filter rows whose 'matleave_95' is not 5, and assign to var m05


```



# 5. Plotting

* Plotting the second rows and all columns except 1st column
* **Question** 為何要`unlist()`？請試著執行`barplot(matleave[2, -1])`這個沒有`unlist()`的版本，看看會有什麼錯誤訊息。資料結構有何差異呢？
* 嘗試用`class()`或`str()`嘗試觀察沒有`unlist()`版本的資料，看看資料型態和有`unlist()`的會有何不同？

## 5.1 Plotting one line

```{r}
# barplot() the second row of m55
# Observing the error msg carefully
barplot(m55[2, ])       # raise error

# barplot() the second row when neglecting the first column
# Observing the error msg carefully
barplot(m55[2, -1])     # raise error

# Inspect the data type of matleave[2, ] by class() for data with or without unlist()
# unlist() to convert a single row data.frame to a vector for barplot()
class(matleave[2, -1])
class(unlist(matleave[2, -1]))


barplot(unlist(m55[2, -1]))
```

* Testing
```{r}
# View(matleave[1]) # select the 1st variable
# View(matleave[ ,1]) # select the 1st column
# View(matleave[1, ]) # select the 1st row

class(m55[1])		# "tbl_df"     "tbl"        "data.frame"
class(m55[ ,1])	# "tbl_df"     "tbl"        "data.frame"
class(m55[1, ])	# "tbl_df"     "tbl"        "data.frame"
class(m55$iso3)	# character (vector)

```




## 5.2 More arguments (args)
```{r}
# barplot() the unlisted second row (neglecting the first col)


# use ?barplot to know more argument of the function.


# Add arguments ylim, space, border, and axat/yaxt one by one to barplot()




```


## 5.3 Plotting multiple lines

* 底下可以看見每一行非常相似且一致的特徵，僅有`matleave`內的索引由1被列出至6。因此，最好的方法是用迴圈（for-loop）的方式將相同的程式碼，從1~6之間做六次。

```{r}
# plot the 1st row


# plot the 2nd to 6th rows


```



## 5.4 for-loop to plot multiple lines 

```{r}
# use for loop and use i as index to barplot multiple subgraphs


```


## 5.5 Sub-plots

* Check `?par` to get paremeters of plotting

* `**mai**`: A numerical vector of the form c(bottom, left, top, right) which gives the margin size specified in inches.

* `**mfcol, mfrow**`:A vector of the form c(nr, nc). Subsequent figures will be drawn in an nr-by-nc array on the device by columns (mfcol), or rows (mfrow), respectively.


```{r}
# use ?par to get more plotting parameters


# use par() to set-up the layout of subgraphs
# use the parameter main=c(0.2, 0.2, 0.2, 0.2) to thrink the padding of figures.
par(mfrow=c(3,2), mai= c(0.2, 0.2, 0.2, 0.2))
for(i in 1:6){
  barplot(unlist(m55[i, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
}

```


## 5.5 Testing

```{r}
# plot more rows to see what happens
par(mfrow=c(3,2), mai= c(0.2, 0.2, 0.2, 0.2))
for(i in 1:10){
    barplot(unlist(m55[i, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
}

# plot all subplots in a figure

```





## 5.6 Plotting m55
```{r}
# nrow() to check number of row of m55.
nrow(m55)

# use par() to set-up plotting parameters.
par(mfrow=c(4, 6), mai= c(0.2, 0.2, 0.2, 0.2))

# use for-loop to plot all graph as subgraph
for (i in 1:nrow(m55)){
  barplot(unlist(m55[i, -1]), border=NA, space=0, xaxt="n", yaxt="n", ylim = c(0,5))
}

```



## 5.7 Adding title to each sub-plot
```{r}
par(mfrow=c(4,6), mai= c(0.2, 0.2, 0.2, 0.2))
for (i in 1:nrow(m55)){
    barplot(unlist(m55[i, -1]), border=NA, space=0,xaxt="n", yaxt="n", ylim = c(0,5))
	title(m55[i,1], line = -4, cex.main=3)
}
```





# Practice02_1_1 Plotting more
```{r}
# plotting matleave_95 != 5 but matleve_13 == 5

# plotting for matleave_13 == 4

```



# Practice02_2_2 selecting and filtering by dplyr I
```{r}
df <- read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T)

# select columns by index
# matleave <- df[ , c(3, 6:24)]


# select all NA cells and assign 0 to them
# matleave[is.na(matleave)] <- 0


# filter rows by condition
# m5 <- matleave[matleave$'matleave_13' == 5, ]


# filter rows by condition
# m55<- m5[m5$'matleave_95' == 5,]


# plot
par(mfrow=c(4,6), mai= c(0.2, 0.2, 0.2, 0.2))
for (i in c(1:nrow(m55))){
	barplot(unlist(m55[i,-1]),
			border=NA, space=0,xaxt="n", yaxt="n", ylim = c(0,5))
	title(m55[i,1], line = -4, cex.main=3)
}
```





# (More) Clean version
```{r}
# readxl::read_excel() to import the xls file
df <- read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T)

# select iso3, and matleave columns by index
matleave <- df[ , c(3, 6:24)]

# str() to inspect the data structure of 
str(matleave)

# select all NA cells and assign 0 to them
matleave[is.na(matleave)] <- 0

# filter rows by condition
m5 <- matleave[matleave$'matleave_13' == 5, ]

# filter rows by condition
m55<- m5[m5$'matleave_95' == 5,]

# plot
par(mfrow=c(4,6), mai= c(0.2, 0.2, 0.2, 0.2))
for (i in c(1:nrow(m55))){
	barplot(unlist(m55[i,-1]),
			border=NA, space=0,xaxt="n", yaxt="n", ylim = c(0,5))
	title(m55[i,1], line = -4, cex.main=3)
}
```



# (More) The fittest version to compute staySame
```{r}
# staySame version
# staySame <- apply(m5[,2:20], 1, function(x) length(unique(x[!is.na(x)]))) 
# m55 <- m5[staySame, ]
# m50 <- m5[!staySame, ]

```





# by dplyr
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
raw <- read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T)
matleave <- select(raw, iso3, 6:24)
m5 <- filter(matleave, matleave_13==5)
m55 <- filter(m5, matleave_95==5)
```


# by dplyr + pipeline
```{r}
m55 <- read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
    select(iso3, 6:24) %>%
    filter(matleave_13==5) %>%
    filter(matleave_95==5)
```



# by dplyr + pipeline + ggplot2

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readxl)

read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>%
	filter(matleave_13==5, matleave_95!=5) %>%
	gather("year", "degree", 2:20) %>%
	replace_na(list(degree=0)) %>%
	mutate(year2=as.POSIXct(strptime(year, "matleave_%y"))) %>%
	mutate(year3 = strftime(year2, "%Y")) %>%
	ggplot() +
	aes(year3, degree) +
    geom_col(color="royalblue", fill="royalblue") + 
	facet_wrap(~ iso3) + 
    theme_void()
	

```




