---
title: "R03_1 Crawling 104"
author: "Jilung Hsieh"
date: "2019/9/2"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Loading essential packages
```{r}
library(tidyverse)
library(httr)
library(jsonlite)
options(stringsAsFactors = F)
```


# Get the first pages

## Must loading the second page
```{r}
# Assigning the 2nd page data url to url2
url2 <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E7%88%AC%E8%9F%B2&order=1&asc=0&page=2&mode=s&jobsource=2018indexpoc"


# Assigning the 3rd page data url to url3
url3 <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E7%88%AC%E8%9F%B2&order=1&asc=0&page=3&mode=s&jobsource=2018indexpoc"

# Getting back the url1 data, assigning to result1
result2 <- fromJSON(content(GET(url2), "text"))

# Tracing variable result2 and finding the data.frame, assigning to df2
df2 <- result2$data$list
```

## Try to get the first page by modifying url
```{r}
# Guessing the 1st page data url to url1
url1 <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E7%88%AC%E8%9F%B2&order=1&asc=0&page=1&mode=s&jobsource=2018indexpoc"

# Getting back the 1st page data
url1 <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E7%88%AC%E8%9F%B2&order=1&asc=0&page=1&mode=s&jobsource=2018indexpoc"
result1 <- fromJSON(content(GET(url1), "text"))
df1 <- result1$data$list
```


## Combine two data with the same variables

```{r}
# all.df <- bind_rows(df1, df2) # will raise error
# Error in bind_rows_(x, .id) : 
#   Argument 31 can't be a list containing data frames
```

## Drop out hierarchical variables
Preserving numeric or character, dropping list of data.frame by assigning NULL to the variable
```{r}
# Drop list and data.frame inside the data.frame
df1$link <- NULL
df1$tags <- NULL
df2$link <- NULL
df2$tags <- NULL

# Re-binding two data.frame df1 and df2
all.df <- bind_rows(df1, df2)
```

## Dropping hierarchical variables by dplyr way
```{r}

# Getting the 1st page data and dropping variable tags and link
# Assigning to df1
df1 <- result1$data$list %>% select(-tags, -link)

# Getting the 2nd page data and dropping variable tags and link
# Assigning to df2
df2 <- result2$data$list %>% select(-tags, -link)

# binding df1 and df2
all.df <- bind_rows(df1, df2)
```


# Finding out the last page number
```{r}
# Tracing the number of pages in result1
last_page_num <- result1$data$totalPage
# Checking the availability of the last page

# Examining if the last page data available by re-composing URL with paste0()
url.last_page <- paste0("https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E7%88%AC%E8%9F%B2&order=1&asc=0&page=", last_page_num, "&mode=s&jobsource=2018indexpoc")

# Getting back and parsing the last page data
result.last_page <- fromJSON(content(GET(url.last_page), "text"))

```

# Using for-loop to get all pages
```{r}
for(p in 1:last_page_num){
    url <- paste0("https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E7%88%AC%E8%9F%B2&order=1&asc=0&page=", p, "&mode=s&jobsource=2018indexpoc")
    result <- fromJSON(content(GET(url), "text"))
    temp.df <- select(result$data$list)
    print(paste(p, nrow(temp.df)))
}
```

# combine all data.frame
```{r}

#  The 1st url of the query
url1 <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E7%88%AC%E8%9F%B2&order=1&asc=0&page=1&mode=s&jobsource=2018indexpoc"

# Getting back the 1st page data
result1 <- fromJSON(content(GET(url1), "text"))

# Tracing and getting total number of page
last_page_num <- result1$data$totalPage

# Truncating hierarchical variables: link and tags
all.df <- select(result1$data$list, -link, -tags)


# for-loop to getting back data and joining them
for(p in 1:last_page_num){
    url <- paste0("https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E7%88%AC%E8%9F%B2&order=1&asc=0&page=", p, "&mode=s&jobsource=2018indexpoc")
    result <- fromJSON(content(GET(url), "text"))
    temp.df <- select(result$data$list)
    all.df <- bind_rows(all.df, temp.df)
    print(paste(p, nrow(all.df)))
}

```







