---
title: "R03_1 Crawling 104"
author: "Jilung Hsieh"
date: "2019/9/2"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Loading essential packages
```{r}
library(tidyverse)
options(stringsAsFactors = F)
library(httr)
library(jsonlite)
```


# Get the first pages

## Must loading the second page
```{r}
# Assigning the 2nd page data url to url2
url2 <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E8%B3%87%E6%96%99%E7%A7%91%E5%AD%B8%E5%AE%B6&order=1&asc=0&page=2&mode=s&jobsource=2018indexpoc"

# Assigning the 3rd page data url to url3
url3 <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E8%B3%87%E6%96%99%E7%A7%91%E5%AD%B8%E5%AE%B6&order=1&asc=0&page=3&mode=s&jobsource=2018indexpoc"

# Getting back the url2 data, assigning to result2
res2 <- GET(url2) %>% content("text") %>% fromJSON()

# Tracing variable result2 and finding the data.frame, assigning to df2
df2 <- res2$data$list

```

## Try to get the first page by modifying url
```{r}
# Guessing the 1st page data url to url1
url1 <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E8%B3%87%E6%96%99%E7%A7%91%E5%AD%B8%E5%AE%B6&order=1&asc=0&page=1&mode=s&jobsource=2018indexpoc"

# Getting back the 1st page data
res1 <- GET(url1) %>% content("text") %>% fromJSON()
df1 <- res1$data$list


```


## Combine two data with the same variables

```{r}
all.df <- bind_rows(df1, df2) # will raise error
# Error in bind_rows_(x, .id) : 
#   Argument 31 can't be a list containing data frames
```

## Drop out hierarchical variables
Preserving numeric or character, dropping list of data.frame by assigning NULL to the variable
```{r}
# Drop list and data.frame inside the data.frame
df1 <- df1 %>% select(-tags, -link)
df2 <- df2 %>% select(-tags, -link)
# Re-binding two data.frame df1 and df2
all.df <- bind_rows(df1, df2)

```

## Dropping hierarchical variables by dplyr way
```{r}

# Getting the 1st page data and dropping variable tags and link
# Assigning to df1


# Getting the 2nd page data and dropping variable tags and link
# Assigning to df2


# binding df1 and df2


```


# Finding out the last page number
```{r}
# Tracing the number of pages in result1
res1$data$totalPage %>% class()


# Checking the availability of the last page
# Examining if the last page data available by re-composing URL with paste0()
url <- paste0("https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E8%B3%87%E6%96%99%E7%A7%91%E5%AD%B8%E5%AE%B6&order=1&asc=0&page=", res1$data$totalPage, "&mode=s&jobsource=2018indexpoc")
url
browseURL(url)

# Getting back and parsing the last page data
res_last_page <- GET(url) %>% content("text") %>% fromJSON()
df <- res_last_page$data$list

```

# Using for-loop to get all pages
```{r}

all.df <- data.frame()

for(i in 1:res1$data$totalPage){
    
    url <- paste0("https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E8%B3%87%E6%96%99%E7%A7%91%E5%AD%B8%E5%AE%B6&order=1&asc=0&page=", i, "&mode=s&jobsource=2018indexpoc")
    print(url)
    res <- GET(url) %>% content("text") %>% fromJSON()
    df <- res$data$list %>%
        select(-tags, -link)
    
    all.df <- all.df %>% bind_rows(df)
    print(nrow(all.df))
}




```

# combine all data.frame
```{r}

#  The 1st url of the query
url1 <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E5%89%8D%E7%AB%AF%E5%B7%A5%E7%A8%8B%E5%B8%AB&order=1&asc=0&page=1&mode=s&jobsource=2018indexpoc"

# Getting back the 1st page data
res1 <- GET(url1) %>% content("text") %>% fromJSON()

# for-loop to getting back data and joining them

all.df <- data.frame()

for(i in 1:res1$data$totalPage){
    
    url <- paste0("https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E5%89%8D%E7%AB%AF%E5%B7%A5%E7%A8%8B%E5%B8%AB&order=1&asc=0&page=", i, "&mode=s&jobsource=2018indexpoc")
    # print(url)
    res <- GET(url) %>% content("text") %>% fromJSON()
    df <- res$data$list %>%
        select(-tags, -link)
    
    all.df <- all.df %>% bind_rows(df)
    message(i, "\t", nrow(all.df))
}

save(all.df, file = "job104_front_end_engineer.rda")
load("job104_front_end_engineer.rda")
```


# NEXT: (In-Class) How to get DCard Relationship forum
```{r}
url_dcard <- "https://www.dcard.tw/f/relationship"
browseURL(url_dcard)
```








