---
title: "R03_7 Parse POST PTT"
author: "Jilung Hsieh"
date: "10/9/2019"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

# loading packages
```{r}
library(tidyverse)
library(httr)
library(rvest)
options(stringsAsFactors = F)
```



# Loading post list with links
```{r}
# Reading post link rds -> posts



```


# Getting one post for examining html structure
```{r}
# WLOG, getting the first post link as an example, assign to -> url


# Getting back the article and parsing as html
# Remember to send cookie




# Verifying the doc by write_html() and browseURL()



```


# Parse one POST
```{r}
# Getting content by CSS selector



# BETTER for the case, Getting content by XPath





# Getting metadata





# Combining data to a data frame
# post.temp <- data_frame(url, pcontent, ptitle, pauthor, ptime)
```


# Using for-loop to get all posts
```{r}

# Create an empty data frame -> all_posts


# for-loop









```


# Practice I. Crawling comments in the for-loop
Modifying the for-loop content to scraping comments for each post. Each iteration of for-loop will scrape and parse multiple comments. Try to bind them together and store all comments in another data frame names "comments."

```{r}

```



# Practice II. Cleaning variables
- Converting posts timestamp to R datetime
- Extracting id and nickname from the author field.
```{r}

```



# Practice III. Writing to rds with timestamp
- Saving posts by `write_rds()`
- Using current time as part of file name.
```{r}
# Getting current time for file name -> current_time


# Converting data type and writing rds


```



