---
title: "TM05_word2vec"
output:
  xaringan::moon_reader:
    self_contained: True
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
---


---
# Word2vec
* https://github.com/bmschmidt/wordVectors
* We will use a `wordVector` package, installing by  `devtools::install_github("bmschmidt/wordVectors")`
* `rword2vec` is another packages for building word2vec model




```{r loading libraries, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(stringr)
library(tidytext)
library(jiebaR)
library(lubridate)
# devtools::install_github("bmschmidt/wordVectors")
library(wordVectors)
options(stringsAsFactors = F)
```




```{r}
segment_not <- c("第卅六條", "第卅八條", "蘇南成")
cutter <- worker()
new_user_word(cutter, segment_not)
stopWords <- readRDS("data/stopWords.rds")
```




```{r loading data}
news.df <- readRDS("data/typhoon.rds") %>%
    filter(!is.na(text)) %>%
    mutate(doc_id = row_number()) %>%
    select(doc_id, everything())
```




```{r tokenization}
tokenized.df <- news.df %>%
    mutate(timestamp=ymd(time)) %>%
    select(-time) %>%
    select(title, text, cat, timestamp, everything()) %>%
    mutate(word = purrr::map(text, function(x)segment(x, cutter)))

unnested.df <- tokenized.df %>%
    select(doc_id, text, word) %>%
    unnest(word) %>%
    filter(!(word %in% stopWords$word)) %>%
    filter(!str_detect(word, "[a-zA-Z0-9]+"))
```







```{r tokenized and save to text}
unnested.df %>% 
    # select(doc_id = sentence_id, word) %>%
	group_by(doc_id) %>%
	summarise(w_w = paste(word, collapse = " ")) %>%
	ungroup() %>%
    .$w_w %>%
	write("text_data.txt")
```


* (deprecated) Alan's code
```
cc$word <- sapply(cc$article, function(x){tryCatch({cutter[x]}, error=function(err){})})
cc$word <- sapply(cc$word,function(x){x[!x %in% stopwords]})
cc$word2 <- sapply(cc$word, function(x){paste(x, collapse = " ")})
#change for word2vec
finaltext <- subset(cc,select="word2")
write.table(finaltext,"text_data.txt")

```





## Training Model
* Once you trained a model, the model can be saved to a `vec.bin` binary file. If you need to use the model again, you needn't rebuild a model, just load the model by `read.vectors(file_name)`.

```{r}
model = train_word2vec("text_data.txt", output="vec.bin",
                       threads = 4, vectors = 300,
                       window =5, min_count = 12,
                       iter=10, force=TRUE)


# model = read.vectors("vec.bin")

```




## plotting model
* `plot(model)` needs `tsne` package (`install.packages("tsne")`).
* Now we still has 300 variables, if we want to plot words on a 2-d plane, we need to reduce the dimension of it to 2-dimension. We use **t-sne** here for dimension reduction.
* Results are scaled down to 2 dimension by t-SNE.
* https://www.codeproject.com/Tips/788739/Visualization-of-High-Dimensional-Data-using-t-SNE
* (option) plotting to a png file: Adding `png('2.png',width = 1500,height = 1500,res=150)` before `plot()`, then adding `dev.off()` after `plot()` to close the plotting target. 

```{r}

# install.packages("tsne")
# library(Rtsne)
# library(tsne)

par(family="STKaiti")
par(family="Heiti TC Light")
plot(model, method = "tsne")
```


## Selecting top 2 dimension as word features
```{r}
model@.Data[,c(1,2)] %>% as.tibble() %>%
    bind_cols(rownames(model@.Data)) %>% 
model[[c("compared", "traditional")]] 

```





# Using the model
* https://github.com/bmschmidt/wordVectors/blob/master/vignettes/introduction.Rmd
* https://github.com/bmschmidt/wordVectors/blob/master/vignettes/exploration.Rmd

```{r}

nearest_to(model,model[["災民"]])
nearest_to(model,model[["政府"]])
nearest_to(model,model[["老天"]])



model %>% closest_to(~ "颱風" - "老天" ,5)
```




## Word clustering
* `model1tex.text`須手動刪除第一列和最後一列的空白
* `rword2vec::bin_to_text()` is used to convert binary file to text file for `read.table()`.
* `rword2vec` is another package for word2vec model
* Install `rword2vec` to convert binary bin to text file for clustering by `devtools::install_github("mukul13/rword2vec")`



```{r}
# library(rword2vec)
rword2vec::bin_to_txt("vec.bin","vec.text")

?readBin
# data <- readBin("vec.bin", character(), endian = "little")
word_vec <- read.table("vec.text",header = F, skip = 1, 
                       quote = "", row.names = NULL,
                       stringsAsFactors = F)
# ?read.table
# head(word_vec)

word_vec[!is.na(word_vec)] <- 0
# word_vec[is.nan(word_vec)] <- 0

#further?---k means clustering
cluster.res <- kmeans(word_vec[,2:301], 50) # time-consuming
word_vec$cluster <- cluster.res$cluster
for(i in 20:30){
  print(paste0("---------------------clueter: ", i))
  print(word_vec$V1[word_vec$cluster==i])
}
```



## unnested to cosine similarity
* Test for computing cosine similarity

```
TCM <- unnested.df %>%
    select(doc_id, w1 = word) %>%
    group_by(doc_id) %>%
    mutate(w2 = lead(w1, 1)) %>%
    ungroup() %>%
    filter(complete.cases(.)) %>% 
    bind_rows(data.frame(doc_id = .$doc_id, w1 = .$w2, w2 = .$w1)) %>%
    count(w1, w2) %>%
    spread(w2, n, fill = 0)

    
```


