---
title: "R01_1 loading data"
author: "Jilung Hsieh"
date: "2019/9/2"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Excuting code in R markdown
* Using `Cmd+Enter` (`Ctrl+Enter` in Window) to excute the line where your cursor is located.
* Using `Cmd(Ctrl)+Shift+Enter` to run all code in a cell

* Using mouse to select multiple lines, then `Cmd(Ctrl)+Shift+c` to comment/uncomment multiple lines.
```{r}
a <- c(1, 2, 3, 4, 5)
b <- 4
a*b
```

## Inserting a new code cell
* Using `Cmd(Ctrl)+Option(Alt)+i` to insert a new cell



# Installing and loading packages
- 套件的使用分為**安裝**和**載入**兩個動作。通常安裝好R的時候就已經安裝好基本`base`套件。當執行R時便會將base套件**預載**入程式的執行環境中。
- 非常多的R使用者會編寫第三方套件，並且將這些套件開放給群眾使用。通常這些套件已經被上載到**R cran**提供下載。而**R cran**上的套件我們可以使用`install.packages("package_name")`來自動安裝到我們的電腦中。


##  Install following packages **at home**
* Remove comment `#` symbol to install new package
```{r install pkgs}
# install.packages("jsonlite")
# install.packages("httr")
```

```{r install these pkgs at home}
# install.packages("tidyverse")
# install.packages("caret")
# install.packages("jiebaR")
# install.packages("topicmodels")
# install.packages("stm")
```



## Loading third-party packages
* 這些第三方套件被安裝好後，還需要被**加載**到程式的執行環境中才可以使用。因此要用`library(package_name)`將其載入。
```{r}
# loading jsonlite and httr library
library(jsonlite)
library(httr)
```


## 註解
* 下列程式碼中開頭有`#`符號者為註解，程式在執行時會自動忽略前面有`#`符號的程式碼。
* 當使用RMarkdown格式撰寫時，因為RMarkdown是在事後才生成文件，所以當遇到要安裝該套件的指令時，便會跳出錯誤訊息。
```{r}
# a <- c(1, 2, 3, 4, 5)
# b <- 4
# a*b
```




# Loading dcard data
* 先不要去管`fromJSON(content(GET(url), "text"))`是什麼意思，先著重在語言的形式。通常一個函式會寫為`func_name()`，所以上述其實是三個函式由內而外一層套一層，從最內層開始往外做。
* 這其實很make-sense，因為如果你有一個數學式`(1 + (3-3)/2)/8`，也是會從最裡面那層做出來。
```{r}
url <- "https://www.dcard.tw/_api/forums/relationship/posts?popular=true"
res <- fromJSON(content(GET(url), "text"))
dplyr::glimpse(res)
head(res)
# View(res)

```




# Getting Taipei theft report data

## Getting from the web directly
```{r}
url <- "http://data.taipei/opendata/datalist/datasetMeta/download?id=68785231-d6c5-47a1-b001-77eec70bec02&rid=34a4a431-f04d-474a-8e72-8d3f586db3df"
df <- read.csv(url, fileEncoding = "big5")
head(df)
dplyr::glimpse(df)
```

## Loading a csv file in data directory
```{r}
# if mac cannot read data
GET(url, write_disk("data/tptheft.csv", overwrite = TRUE))
df <- read.csv("data/tptheft.csv", fileEncoding = "big5")
head(df)
```


# Loading MOI data through API
```{r}
url <- "https://www.ris.gov.tw/rs-opendata/api/v1/datastore/ODRP024/107?page=1"
first_page <- fromJSON(content(GET(url), "text"))
head(first_page$responseData)
```




# Getting 104 query data
```{r}
url <- "https://www.104.com.tw/jobs/search/list?ro=0&kwop=7&keyword=%E7%88%AC%E8%9F%B2&order=1&asc=0&page=3&mode=s&jobsource=2018indexpoc"

res <- fromJSON(content(GET(url), "text"))
df <- res$data$list
head(df)
```




# Getting ubike
- https://taipeicity.github.io/traffic_realtime/
```{r}
url <- "https://tcgbusfs.blob.core.windows.net/blobyoubike/YouBikeTP.json"
ubike.list <- fromJSON(content(GET(url),"text", encoding = "utf-8"))
ubike.v <- unlist(ubike.list$retVal)
ubike.m <- matrix(ubike.v, byrow = T, ncol = 14)
ubike.df <- as.data.frame(ubike.m)
names(ubike.df) <- names(ubike.list$retVal$`0001`)
head(ubike.df)
```

